---
title: "COVID-19"
date: "4/17/2020"
output: ioslides_presentation
---

## App Idea

> The main idea of the app is to provide interactive and quick indicators for COVID19 data

## Data Source

> The data is obtained from [JHU](github.com%2FCSSEGISandData%2FCOVID-19&usg=AOvVaw1vKpECdLTiTa7d-LqfWRs0) <3

## Main Features
- Find the overall trends globally and for each country.
- Can compare many countries together
- Find the sum of active. confirmed, death and recovered cases.
- Find the time trend of active confirmed, death and recovered cases.
- Interative charts where you can zoom and pan
- Interactive tables where you can sort the data as you want.

## Limitations
- The app is terrible slow and need some optimization.
- Their is no feature to compare a country to the global total trend or averages.

## Example of Interactive chart
You can selet hover over the bars to see the counts, press on the country legend to hide other, zoom and pane!
```{r echo=FALSE, message=FALSE, warning=FALSE}
source("data.R")
library(plotly)
dat <- dat %>% group_by(Country.Region) %>% filter(Country.Region %in% c("US", "Finland", "Algeria", "Egypt")) %>% 
      summarize(Confirmed = sum(Confirmed, na.rm = T)) 

 g <- dat%>% ggplot()
  

ggplotly(g + geom_bar(aes(y = Confirmed, x = Country.Region, fill = Country.Region), stat = 'identity'))

```


## Example of Interactive table
In this table you can have more control to compare between countries in the time frame you have selected from the navigation of the app
```{r echo=FALSE, message=FALSE, warning=FALSE}
DT::datatable(dat)
```


